Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-25 ms.tex
fixing rad

\begin{figure}
  \includegraphics[width=\columnwidth]{cooling.eps}
  \caption{\label{fig:cooling} Ratio of the rate of heating to
radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a
function of radius (solid lines) for each of our solutions shown in
Figure \ref{fig:profiles}.  Dashed lines show for comparison the ratio
of the cooling to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
For high heating rates both ratios are approximately equal at the
stagnation radius (marked as squares).  When $\dot{q}_{\rm
heat}/\dot{q}_{\rm cool} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff}
\lesssim 10$, the flow is susceptible thermal instabilities.  {\bf
BDM: change y axis labels to qdotheat/qdotrad, tcool/tff}.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
\caption{\label{fig:vwSourcesImp} Different sources contributing to the gas heating rate in galactic nuclei at time $\tau_{\star}$ after a single burst of star formation.  Top and bottom panels show cases for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$, respectively.  Solid and dashed lines show the ranges of $\tau_{\star}$ for which the accretion flow is thermally stable and unstable, respectively, according to the ratio of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius (eq.~[\ref{eq:cooling3}]).   Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}. {\bf BDM: change x axis range so lines start at 3e6 yr }}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{cooling.eps}
  \caption{\label{fig:cooling} Ratio of the rate of heating to
radiative cooling, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$, as a
function of radius (solid lines) for each of our solutions shown in
Figure \ref{fig:profiles}.  Dashed lines show for comparison the ratio
of the cooling to the free-fall timescale $t_{\rm cool}/t_{\rm ff}$.
For high heating rates both ratios are approximately equal at the
stagnation radius (marked as squares).  When $\dot{q}_{\rm
heat}/\dot{q}_{\rm rad} \lesssim 1$ and/or $t_{\rm cool}/t_{\rm ff}
\lesssim 10$, the flow is susceptible thermal instabilities.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
\caption{\label{fig:vwSourcesImp} Different sources contributing to the gas heating rate in galactic nuclei at time $\tau_{\star}$ after a single burst of star formation.  Top and bottom panels show cases for black hole masses of $\Mbh=10^6 \Msun$ and $\Mbh= 10^8 \Msun$, respectively.  Solid and dashed lines show the ranges of $\tau_{\star}$ for which the accretion flow is thermally stable and unstable, respectively, according to the ratio of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ near the stagnation radius (eq.~[\ref{eq:cooling3}]).   Also shown with horizontal gray lines are the velocity dispersions according to $\Mbh-\sigma$ \citep{Gultekin+09}.}
\end{figure}
